TacticToe: Learning the Game of Tactics

### 2018-02-07 tactictoe_jv.tex
commenting out section 7.3 on increasing Tactictoe's knowledge (delaying decision to remove it)

%sh stats.sh MNM_AE2I
%273 203 3 67 0
%thibault@grid02:~/big$ sh stats.sh MNM_AE2
%273 203 3 67 0
%thibault@grid02:~/big$ sh stats.sh MNM_AE4
%273 201 3 69 0
%thibault@grid02:~/big$ sh stats.sh MNM_AE4I
%273 200 3 70 0
%thibault@grid02:~/big$ sh stats.sh MNM_AE1
%273 198 3 72 0
%thibault@grid02:~/big$ sh stats.sh MNM_AE1I
%273 200 3 70 0

%thibault@grid02:~/big$ sh stats.sh MNM_ATPE
%273 213 3 57 0
%thibault@grid02:~/big$ sh stats.sh MNM_ATPM01
%273 216 3 54 0
%thibault@grid02:~/big$ sh stats.sh MNM_ATPM01E
%273 218 3 52 0
%thibault@grid02:~/big$ sh stats.sh MNM_ATPM02
%273 212 3 58 0
%thibault@grid02:~/big$ sh stats.sh MNM_ATPM04
%273 212 3 58 0

%thibault@grid02:~/big$ sh ftim.sh MNM_O40
%127
%9
%8
%2
%2
%148
%thibault@grid02:~/big$ sh ftim.sh MNM_O10
%124
%15
%5
%3
%1
%148
%thibault@grid02:~/big$ sh ftim.sh MNM_ON
%108
%16
%6
%3
%6
%thibault@grid02:~/big$ sh ftim.sh MNM_T005
%124
%13
%5
%2
%3

\begin{table}[ht]
\centering\ra{1.3}
\small
\begin{tabular}{llcc}
\toprule
 Technique & Parameters & Solved (1s) & Solved (60s)\\
\midrule
Tactic time out & 0.02s && 154\\
                & 0.05s (default) && 156\\
                & 0.1s && 154\\
\midrule
Orthogonalization & none & 105 & 156 \\
                  & $radius = 10$ & 121 & 156 \\
                  & $radius = 20$ (default) & 121 & 156 \\ 
                  & $radius = 40$ & 124 & 156 \\
\midrule
Abstraction       & none (default)  && 156\\ 
                  & $theorems = 8$  && 195\\
                  & $theorems = 16$ && 199\\
                  & $theorems = 32$ && 195\\
\midrule
MCTS policy & $c_{policy} = 0.4$ && 149\\
            & $c_{policy} = 0.5$ (default) && 156\\
            & $c_{policy} = 0.6$ && 153\\

\midrule
MCTS evaluation & none (best abstraction) && 199\\
				& $c_{exploration} = 1$ && 201\\ 
				& $c_{exploration} = 2$ && 203\\ 
				& $c_{exploration} = 4$ && 198\\
\midrule
ATP integration & none (best MCTS evaluation) && 203\\
                & \metis 0.1s && 216\\
                & \metis 0.2s && 212\\
                & \metis 0.4s && 212\\ 
                & \eprover && 213\\
                & \metis 0.1s + \eprover && 218\\
\bottomrule
\end{tabular}
\end{table}

Say the respective percentage after 5seconds for orthogonalization.

@@

%\todo{decide to keep this section or not}

@@

%the low 
%success rate of the
%default strategy.} 

@@

%\paragraph{Self-learning}\todo{explain better or remove or move to future work}
%All our feature vectors have been learned form human proofs. We now can now 
%also add tactic-goal pairs that appears in final \tactictoe's proof. To 
%prevent 
%duplication of effort, orthogonalization of those 
%tactics is essential to have a beneficial effect.
%Since recording and re-proving are intertwined, the additional data is 
%available for the next proof search.
%The hope is that the algorithm will improve faster by learning from its own 
%discovered proofs than from the human proof 
%scripts~\cite{DBLP:conf/cade/Urban07}. Side experiments indicate that 
%self-learning improves \tactictoe's success rate by less than one percent.

>>>>

\begin{table}[ht]
\centering\ra{1.3}
\small
\begin{tabular}{llcc}
\toprule
 Technique & Parameters & Solved (1s) & Solved (60s)\\
\midrule
Tactic time out & 0.02s && 154\\
                & 0.05s (default) && 156\\
                & 0.1s && 154\\
\midrule
Orthogonalization & none & 105 & 156 \\
                  & $radius = 10$ & 121 & 156 \\
                  & $radius = 20$ (default) & 121 & 156 \\ 
                  & $radius = 40$ & 124 & 156 \\
\midrule
Abstraction       & none (default)  && 156\\ 
                  & $theorems = 8$  && 195\\
                  & $theorems = 16$ && 199\\
                  & $theorems = 32$ && 195\\
\midrule
MCTS policy & $c_{policy} = 0.4$ && 149\\
            & $c_{policy} = 0.5$ (default) && 156\\
            & $c_{policy} = 0.6$ && 153\\
\midrule
MCTS evaluation & none (best abstraction) && 199\\
				& $c_{exploration} = 1$ && 201\\ 
				& $c_{exploration} = 2$ && 203\\ 
				& $c_{exploration} = 4$ && 198\\
\midrule
ATP integration & none (best MCTS evaluation) && 203\\
                & \metis 0.1s && 216\\
                & \metis 0.2s && 212\\
                & \metis 0.4s && 212\\ 
                & \eprover && 213\\
                & \metis 0.1s + \eprover && 218\\
\bottomrule
\end{tabular}
\caption{\label{tab:tuning} Number of problem solved with different set of 
parameters for \tactictoe on a training set of 273 theorems.} 
\end{table}

@@

%\todoi{decide to keep or not}

@@

%the low success rate of thedefault strategy.} 

@@

\paragraph{Self-learning}\todo{explain better or remove or move to future work}
All our feature vectors have been learned form human proofs. We now can now
also add tactic-goal pairs that appears in final \tactictoe's proof. To prevent
duplication of effort, orthogonalization of those
tactics is essential to have a beneficial effect.
Since recording and re-proving are intertwined, the additional data is
available for the next proof search.
The hope is that the algorithm will improve faster by learning from its own
discovered proofs than from the human proof
scripts~\cite{DBLP:conf/cade/Urban07}. Side experiments indicate that
self-learning improves \tactictoe's success rate by less than one percent.
